Numerical trajectory patterns of floating macroalgae

### 2020-11-25 thesis_chapter_3.Rmd
added script for lat and lon analysis

library(ggplot2)
library(rgdal)
library(tidyverse)
library(viridis)
library(gridExtra)
library(ggpubr)
#library(ggord)
library(vegan)
library(dplyr)
library(ggpubr)
library(maps)
library(flextable)
library(officer)
library(tidync)
library(tidyverse)
library(hexbin)
s
```

@@

```{r eddy plots, message=FALSE, warning=FALSE, include=FALSE}

passive_eddy <- ggplot() + 
  geom_point(data = p_eddy, aes(x = lon, y = lat)) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Passive") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

min_eddy <- ggplot() + 
  geom_point(data = Min_K_Eddy, aes(x = lon, y = lat)) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Minimum Ac") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

mean_eddy <- ggplot() + 
  geom_point(data = Mean_KFloat_Eddy, aes(x = lon, y = lat)) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Mean Ac") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

max_eddy <- ggplot() + 
  geom_point(data = Max_KFloat_Eddy, aes(x = lon, y = lat)) +
  xlab("Longtitude") + 
  ylab("Latitude") +
  ggtitle("Maximum Ac") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggarrange(passive_eddy, min_eddy, mean_eddy, max_eddy)
```

@@

```{r path plots, warning=FALSE, message=FALSE, echo=FALSE}

@@

>>>>

library(ggplot2)
library(rgdal)
library(tidyverse)
library(viridis)
library(gridExtra)
library(ggpubr)
#library(ggord)
library(vegan)
library(dplyr)
library(ggpubr)
library(maps)
library(flextable)
library(officer)
library(tidync)
library(tidyverse)
library(hexbin)

@@

```{r eddy plots, message=FALSE, warning=FALSE, include=TRUE, echo=FALSE}

total_eddy <- rbind(p_eddy, Min_KFloat_Eddy, Mean_KFloat_Eddy, Max_KFloat_Eddy)

ggplot() + 
  geom_point(data = total_eddy, aes(x = lon, y = lat, color = type)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

@@

@@

```{r path plots, warning=FALSE, message=FALSE, echo=FALSE, include=TRUE}

@@

```{r trajectory plots, echo=FALSE, message=FALSE, warning=FALSE}

total_mean_traj <- total_data %>% #calculate mean trajectory 
  group_by(t, type) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

lon_plot <- ggplot() +
  geom_point(data = total_mean_traj, aes(x = t, y = lon, color = type)) +
  xlab("Time") +
  ylab("Longitude") +
  theme_bw() +
  guides(fill=guide_legend(title="Type"))

lat_plot <- ggplot() +
  geom_point(data = total_mean_traj, aes(x = t, y = lat, color = type)) +
  xlab("Time") +
  ylab("Latitude") +
  theme_bw() +
  guides(fill=guide_legend(title="Type"))

ggarrange(lon_plot, lat_plot, labels = "AUTO", common.legend = TRUE, ncol = 1, nrow = 2, legend = "right")
